DATA 621---Business Analytics and Data Mining

### 2020-09-10 HW1/HW1_AF.Rmd
updating grammar

We are given a data set containing 2,276 records, each of which includes the 
number of wins the team had during a particular year and 15 additional statistics 
about the season. The team wins on average about 50% of the games they play (81 games 
out of 162), with the best season having 146 wins and the worst season having 
0 wins. The data is pretty normally distributed and most seasons have between
49 and 112 wins (blue lines below). This means that there aren't too many extreme 
seasons where the team won significantly more or significantly less games than 
usual. This serves as a good gut-check for our final predictions; if the 
predicted wins are too high or too low, we know something is probably off.

>>>>

We are given a data set containing 2,276 records, each of which includes 15 statistics
and the total number of wins a team had in a given year. On average, the team wins about 
50% of the games they play (81 games out of 162), with the best season having 146 wins 
and the worst season having 0 wins. The data is normally distributed and most seasons have 
between 49 and 112 wins (blue lines below). This means that there aren't too many extreme 
seasons where the team won significantly more or significantly less games than usual. This 
serves as a good gut-check for our final predictions; if the predicted wins are too high or 
too low, we know something is probably off.
